Notebook of learning from ensemble labels

### 2021-08-14 docs/notebook_learn_dl_ensemble.Rmd
Revert back to regular unet

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_200epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

@@

python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard14/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard14/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

>>>>

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 221 --tain_batch_size 16
```

@@

python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard14/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard14/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```
